Predictors of frog survival following translocations - analyses

### 2022-11-09 code/translocation_survival_analysis.Rmd
Address #10, make effect plots with confidence bands

# use untransformed predictor (elevation) to make plot easier to interpret  
d1_elevz %>% 
  select(site_id, translocation_id, snowt1_z, elev_z, elevation, male_c, donor, surv) %>% 
  add_epred_draws(m1d_reduce, ndraws = 100, re_formula = NA) %>% 
  ggplot(aes(x = elevation, y = surv)) +  #   "ggplot(aes(x = (elev_z * 2*sd_elev) + mean_elev, y = surv)) +" gives identical result
    geom_line(aes(y = .epred, group = .draw), color = "blue", size = 0.2, alpha = 0.5) +
    # geom_point(aes(y = .epred)) +
  labs(x = "Elevation of recipient site (meters)", y = "Probability of 1-year frog survival")
```

>>>>

# use untransformed predictor (elevation) to make plot easier to interpret  
d1_elevz %>% 
  select(site_id, translocation_id, snowt1_z, elev_z, elevation, male_c, donor, surv) %>% 
  add_epred_draws(m1d_reduce, ndraws = 100, re_formula = NA) %>% 
  ggplot(aes(x = elevation, y = surv)) +  #   "ggplot(aes(x = (elev_z * 2*sd_elev) + mean_elev, y = surv)) +" gives identical result
    geom_line(aes(y = .epred, group = .draw), color = "blue", size = 0.2, alpha = 0.5) +
    # geom_point(aes(y = .epred)) +
  labs(x = "Elevation of recipient site (meters)", y = "Probability of 1-year frog survival")

# Plot with confidence bands
alpha = 1 - 0.95
d1_elevz %>% 
  select(site_id, translocation_id, snowt1_z, elev_z, elevation, male_c, donor, surv) %>% 
  add_epred_draws(m1d_reduce, ndraws = 1000, re_formula = NA) %>% 
  group_by(elevation) %>%
  summarise(lower=quantile(.epred, alpha), 
            upper=quantile(.epred, 1 - alpha),  
            med=quantile(.epred, 0.5)) %>%
  ggplot(aes(x=elevation)) + 
          geom_line(aes(y = med), color = "blue", size = 1, alpha = 0.8) +
          geom_ribbon(aes(ymin=lower, ymax=upper), fill="blue", alpha=0.1) +
          labs(x = "Elevation of recipient site (meters)", y = "Probability of 1-year frog survival") +
          theme_classic()
```
